Rodent trapping studies to understand the prevalence of zoonotic disease in West Africa: A scoping review.

### 2021-09-05 reports/manuscript_v2.Rmd
improving fig. 5

---
title: "Rodent trapping studies to understand the prevalence of zoonotic disease in West Africa: A scoping review."
description: |
date: "`r Sys.Date()`"
author: 
  - first_name: "David"
    last_name: "Simons"
    url: https://www.dsimons.org
    orcid_id: 0000-0001-9655-1656
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
  word_document:
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: "`r here::here('citations', 'manuscript_citations.bib')`"
---
```{r, echo=FALSE}
source(here::here("scripts", "manuscript_library.R"))
```

@@

```{r, figure_1, layout = "l_page", echo=FALSE}
study_timings <- read_rds(here("plots", "study_timings.rds"))

plot_grid(study_timings)

@@

```{r, figure_2, layout = "l_page", echo=FALSE}
knitr::include_graphics(here("figures", "Figure_2.png"))
```

@@

```{r, figure_3, layout = "l_page", echo=FALSE}
knitr::include_graphics(here("figures", "Figure_3.png"))
```

@@

```{r figure_5, layout = "l_page", echo=FALSE}

@@

Figure 5 - Matrix heat plot Y - rodent species/genera, X - pathogen species/genera. Colour relates to proportion positive (Perhaps use bivariate colour to also highlight the number of test performed in that species).

>>>>

---
title: "Rodent trapping studies to understand the prevalence of zoonotic disease in West Africa: A scoping review."
description: |
date: "`r Sys.Date()`"
author: 
  - first_name: "David"
    last_name: "Simons"
    url: https://www.dsimons.org
    orcid_id: 0000-0001-9655-1656
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
  # word_document:
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = here::here())
  })
always_allow_html: yes
bibliography: "`r here::here('citations', 'manuscript_citations.bib')`"
---
```{r, echo=FALSE}
source(here::here("scripts", "manuscript_library.R"))
```

@@

```{r, figure_1, layout = "l_page", echo=FALSE}

knitr::include_graphics(here("figures", "Fig_1_Panel_A.png"))

@@

```{r, figure_2, layout = "l-screen-inset", echo=FALSE}
knitr::include_graphics(here("figures", "Figure_2.png"))
```

@@

```{r, figure_3, layout = "l-screen-inset", echo=FALSE}
knitr::include_graphics(here("figures", "Figure_3.png"))
```

@@

```{r figure_5, layout ="l-screen-inset", echo=FALSE}

@@

*Figure 5*: The percentage of assays from each included species and microorganism tested for is represented by colour. The size of a point relates to the squareroot of the number of individuals assayed. The plot on the left is for species/genera assayed for four or more microorganisms, the plot on rights are for species/genera assayed for 3 or less microorganisms.
